%-------------------------
% Resume in Latex
% Author : Pratyay Gopal
% Based off of: https://gthub.com/sb2nov/resume
% License : MITi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Pratyay Gopal Reddy Rudravaram} \\ \vspace{1pt}
    \href{mailto:pratyay2@illinois.edu}{\underline{pratyay2@illinois.edu}} $|$ 
    \href{https://linkedin.com/in/pratyay-gopal}{\underline{linkedin.com/pratyay-gopal}} $|$
    \href{https://github.com/pratyaygopal}{\underline{github.com/pratyaygopal}} $|$
    \small US Citizen $|$ 
\end{center}

    \vspace{-20pt}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Illinois Urbana Champaign}{GPA: 3.72}
      {Bachelor of Sciences in Computer Engineering - James Scholar Honors}{Expected December 2026}
    
  \resumeSubHeadingListEnd
    \begin{itemize}
    \setlength\itemsep{-5pt}
    \item \textbf{Relevant Coursework} : Computer Systems Engineering, Digital Logic, FPGA, Paralell Programming, Data Structures, Electronics, Analog Signal Processing, Linear Algebra, Discrete Math
    \item \textbf{Organizations} : SigArch, Department of ECE, IEEE, Association for Computing Machinery
    \end{itemize}

    \vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: SystemVerilog, Verilog, C, C++, VHDL, Python, Java}\\ 
     \textbf{Tools}{: Git, Docker, Raspberry Pi, Arduino, KICAD, ORCAD, PADS, Altera Quartus, Vivado Xilinx, FL Studio, VS Code, PyCharm, IntelliJ} \\
     \textbf{Certifications}{: VMware Certified Professional (VCP-DCV), VCTA, AWS Solutions Architect – Associate, ISC2 CC} \\
      \textbf{Misc}{: Linux, Virtualization, Bash, Pspice}
    }}
 \end{itemize}

    \vspace{-15pt}
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Apollo Computing Laboratories}{June 2024 -- August 2024}
      {Hardware Design Intern}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed a power delivery board from concept to completion for high availability data-center applications.}
        \resumeItem{Working on programming FPGA boards deployed in mission critical infrastructure using Verilog and VHDL.}
        \resumeItem{Operated an automated SMD production line to assemble defense related PCBs.}
        
      \resumeItemListEnd
      
    \resumeSubheading
      {Grainger College of Engineering, ECE}{January 2024 -- Present}
      {Course Staff (Digital Logic)}{Urbana, IL}
      \resumeItemListStart
        \resumeItem{Assessed student assignments weekly and provided constructive feedback and handled regrade requests.}
        \resumeItem{Corrected rubrics for Digital Logic Design Homework problems that did not have streamlined solutions.}
        \resumeItem{Collaborated with ECE department faculty to develop a better homework structure to ensure faster grading.}
      \resumeItemListEnd
      
\begin{comment}
    \resumeSubheading
      {ECE 220 Grader}{August 2024 -- Present}
      {University of Illinois Urbana Champaign}{Urbana, IL}
      \resumeItemListStart
        \resumeItem{Became a Grader for ECE220 (Intro to Computing Class) for getting an A with honors in the class}
        \resumeItem{Helped grade the Homework and exams of 300+ students taking the course}
      \resumeItemListEnd
\end{comment}

    \resumeSubheading
      {Thermo Fisher Scientific}{May 2022 – June 2022}
      {Embedded Engineering Intern}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Coded a Raspberry pi test-bench to calibrate a thermocouple for blood bank temperature regulation using python.}
        \resumeItem{Simulator was deployed to 10+ locations across India and was used to calibrate blood bank coolers for a lower cost}
        \resumeItem{Maintained and updated a spreadsheet of testing data for 100+ trials gathered from SPICE simulation.}
    \resumeItemListEnd

\begin{comment}
    \resumeSubheading
         {Intern}{January 2020 – May 2022}
      {RCV Innovations PVT LTD}{Hyderabad, India}
        \resumeItemListStart
        \resumeItem{Organized Inventory of 100+ unique computer parts and learned how to build servers and PCs.}
     \resumeItemListEnd
\end{comment}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{FPGA Video Game Port} $|$ \emph{Vivado, FPGA, SPI, HDMI}}{}
          \resumeItemListStart
            \resumeItem{Ported a modified version of "Five Nights At Freddys" on a Spartan-7 based Urbana Board FPGA.}
            \resumeItem{Created all of the game logic and graphics running at 55 Hz through HDMI and utilizes 270kB of RAM.}
            \resumeItem{Optimized FPGA performance by reducing number of registers, BRAM, and LUTs required for design.}
            \resumeItem{Demoed at the invite only ECE 385 showcase due to the complexity of the project.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Power Delivery Board} $|$ \emph{Orcad, PADS}}{}
          \resumeItemListStart
            \resumeItem{Designed a server power delivery board to power storage bays using a server power supply.}
            \resumeItem{Used Orcad and PADS for design and layout and gained PCB design experience.}
            \resumeItem{Verified and tested the final board after manufacturing to ensure that it works as intended.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Breadboard Synth} $|$ \emph{Falstad, Arduino, Oscilloscopes}}{}
          \resumeItemListStart
            \resumeItem{Generated and Implemented 4 synth modules for a fully modular music synthesizer for the ECE198 Honors lab.}
            \resumeItem{Used Falstad for design and worked with electrical workbench tools for testing.}
            \resumeItem{Created an arduino testbench with 10+ modes to callibrate the tones notes.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Temperature Regulation Calibrator} $|$ \emph{Raspberry Pi, Python, ADC/DAC}}{}
          \resumeItemListStart
            \resumeItem{Built a proof of concept of an affordable, temperature calibrator using thermocouples and Raspberry Pi.}
            \resumeItem{Coded the functionality for calibrating the thermocouple using python and designed a circuit for the project.}
            \resumeItem{Ran 100+ simulations of the ADC/DAC and recorded data to ensure minimal variance in the output voltage.}
            \resumeItem{Github repo: https://github.com/pratyaygopal/Thermocouple-Simulator}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Linux Migration} $|$ \emph{Linux, Windows, Virtualization}}{}
          \resumeItemListStart
            \resumeItem{Improved the performance, security and stability of 30 computers by upgrading Windows(7/XP) to Linux Mint.}
            \resumeItem{Created admin groups for privileged system access during computer based tests to monitor the students.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
